\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage{makecell}
\usepackage[margin=0.7in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage[normalem]{ulem}

\renewcommand\theadalign{bc}
\renewcommand\theadfont{\bfseries}
\renewcommand\theadgape{\Gape[4pt]}
\renewcommand\cellgape{\Gape[4pt]}

\usepackage[
backend=biber,
style=numeric,
sorting=ynt
]{biblatex}

\addbibresource{dissertationbib.bib}

%opening
\title{Software Proposal Document for project ————}
\author{Ahmed Mohamed, Mohamed Ahmed ,....}

\begin{document}
\maketitle
\begin{table}[htp]

\begin{tabular}{|l|l|l|}
\hline
\thead{Proposal Version}    & \thead{Date} & \thead{Reason for Change}  \\ \hline
1.0 & 12-April-2020   & \makecell{Proposal First version’s specifications are defined}   \\ \hline
1.1 & 20-April-2020   & \makecell{Scope updated} \\ \hline
\end{tabular}
\caption{Document version history}
\end{table}

\begin{table}[htp]
\begin{tabular}{cc}
\thead{GitHub:}    & {........................................................}   
\end{tabular}
\end{table}


\begin{abstract}
The main idea of this project is to study the ........
(Word Limit 150)
\end{abstract}

\section{Introduction}
\subsection{Background}
Please start from very big domain for your problem then focus on some area inside this domain that match your interest.
\subsection{Motivation}
\subsubsection{Academic}
Discuss Academic Needs for your project. You must include references.
\subsubsection{Business}
Discuss business Needs for your project.

\subsection{Problem Statement}
Please put a focus on 1-2 challenges that this project aims to solve and state them very clear as your formal problem statement.

\section{Project Description}
Show down with a figure the proposed system.
\subsection{Objectives}
Why this system is to be developed.
\subsection{Scope}
The scope of your project.
\subsection{Project Overview}
Some extra details for your system implementations.
\subsection{Stakeholder}
\subsubsection{Internal}
State who is the team leader. list all team members with their responsibilities
\subsubsection{External}
State who are the End Users and clients

\section{Similar System}
\subsection{Academic}

List down at least 10 papers from ACM and IEEE for similar work experience in the domain of your problem. You can add 5 papers or more from other sources (Springer, Elsevier,  ..etc)

Be sure that each paper you list include the following points

\begin{enumerate}
\item The main problem statement of the work.
\item How the researchers contributed to solve the problem
\item The dataset used by the researchers
\item What main results the researchers reach.
\item Criticize the paper
\item figure if possible
\end{enumerate}

\subsection{Business Applications}
Describe available business applications the the market with figures. (Optional)

\section{What is new in the Proposed Project?}

\section{Proof of concept}
Explain the 10\% implemented in your project so far.

\section{Project Management and Deliverables}
\subsection{Tasks and Time Plan}
Use some software for primitive plan of your project.
\subsection{Budget and Resource Costs}

\section{Supportive Documents}
Add sections covering one or more of the following:
\begin{itemize}

\item Dataset.
\item Contact documents
\item users/survey
\item Contacting authors.

\end{itemize}

\section {References}
20 Reference Minimum (80\% Academic)
\printbibliography
\end{document}
